---
title: A new website - R Markdown
date: '2020-05-07T13:36:26+02:00'
slug: second-post
categories: []
tags: []
subtitle: ''
summary: A post in R Markdown
authors: [Sebastiaan de Klerk]
lastmod: '2020-05-07T22:59:58+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---
This website has been created using [RStudio](https://www.rstudio.com/), specifically the Blogdown package, that 
can be installed in R using the following piece of code:
```{r, eval = FALSE}
install.packages("blogdown")
```

The package can be loaded in the RStudio global environment by using:
```{r, eval = FALSE}
library(blogdown)
```

The nice thing about building websites in R is that the text can be made up in Markdown, and 
R Markdown. Which allows you to present code, as seen above. You can also give commments with the code,
like this:
```{r}
1 + 1 #executed
```

It is important to note that there are two types of Markdown. The regular Markdown does not
allow any execution of code, while R Markdown does allow execution of code. For example,
this post has been written in R Markdown, and therefore 1 + 1 is calculated.
Based on what you want to display on the website, it is important to decide which type
of Markdown to use.In the other post, with almost the same title and content, I have used Markdown in stead of R Markdown. You can see the difference in the other post: 1 + 1
is not calculated!

This website is hosted by [Netlify](https://www.netlify.com/), and the files that make up this website are available on my GitHub [account](https://www.github.com/Sebastiaan1986). The website is powered by
the Academic theme for Hugo. I have used [Disqus](https://www.disqus.com) to 
enable commenting, as can be seen below. Finally, if you want to build a website in R,
a good place to start is [here](https://bookdown.org/yihui/blogdown/).

I will use this website to update you about the projects that I am working on!


